Rationality, Evolution \& the Environment

### 2015-10-06 paper/paper.tex
paper sec 3 rewrite

We would like to put this latter idea to the test. We present a formal argument intended to
support the conclusion that subjective preferences that differ from objective fitness can be
adaptive. This is brought to the foreground if we acknowledge the potential mutual dependence
of subjective preferences and subjective beliefs in adaptationist approaches to decision
making. More specifically, we show that subjective, non-veridical preference representations
based on a notion of regret
\citep[e.g.][]{Savage1951:The-theory-of-s,LoomesSugden1982:Regret-Theory:-}\todo{add
  references?}\ can be adaptive and even outperform objective, veridical representations of the
actual fitness, when agents, at least on occasion, hold imprecise probabilistic beliefs
(CITE).

@@

The following Section~XYZ will introduce the basic notions needed in the remainder. Section~XYZ
details our method of using ``meta-games''. \dots

\section{Basic notions}
\label{sec:basic-notions}

@@

With some due simplification, there are two types of approaches to solving games: one focuses
on the individual agents' perpectives and gives \emph{choice rules}, another considers sets of
choices of all agents that are, in some sense or other, locked-in. Let's look at either in
turn, to the extent necessary for this paper:

@@

\paragraph{Equilibrium \& stability.}

\begin{itemize}
\item \textcolor{red}{add here:}
  \begin{itemize}
  \item NE, strict, weak
  \item ESS, NSS
  \end{itemize}
\end{itemize}

\todo[inline]{should we also include here: dominance}

@@

>>>>

We would like to put this latter idea to the test. We present a formal argument intended to
support the conclusion that subjective preferences that differ from objective fitness can be
adaptive. We argue that it is important to take into account the potential mutual dependence of
subjective preferences and subjective beliefs in adaptationist approaches to decision
making. More specifically, we show that subjective, non-veridical preference representations
based on a notion of regret
\citep[e.g.][]{Savage1951:The-theory-of-s,LoomesSugden1982:Regret-Theory:-}\todo{add
  references?}\ can be adaptive and even outperform objective, veridical representations of the
actual fitness, when agents, at least on occasion, hold imprecise probabilistic beliefs (CITE)
and make decisions based on a security choice rule (here: the maximin rule).

@@

The following Section~XYZ will introduce the choice mechanisms that we will focus in on in the
remainder. Section~XYZ details our method of using ``meta-games''. \dots

\section{The cast}
\label{sec:basic-notions}

@@

With some due simplification, there are two types of approaches to solving games: one focuses
on the individual agents' perpectives and gives \emph{choice rules}, another considers sets of
choices of all agents that are, in some sense or other, locked-in. We will look at the former
here; the latter will be relevant only later, when turn to evolutionary competition between
choice mechanisms in Section~\ref{sec:model}.\footnote{We make a subtle distinction here
  between \emph{choice rules} and \emph{choice mechanisms}: the former refers to a function of
  mapping (subjective) preferences and uncertainty unto choices of acts; the latter is more
  encompassing and contains the choice rule, together with the particular way of forming or
  representing preferences and uncertainty.}

@@

@@

Before we turn to evolutionary competition between choice mechanisms, we should justify our
focus on the two choice rules. In the following we argue that both the minimax rule, as well as
the Laplace rule can be viewed as the same choice rule under different representations of
uncertainty.
